---
title: "Analysis for ensemble"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# Set path
if (Sys.info()["sysname"] == "Darwin"){
  mount_path <- "/Volumes/"
} else if (Sys.info()["sysname"] == "Linux"){
  mount_path <- "/mnt/"
} else {
  stop("Operating system is not supported")
}
```

load data
```{r}
results <- read.csv("./data/results_all_models.csv")
```


compute correctness of pred per model and per label
```{r}
library(tibble)
library(dplyr)

eval <- results %>%
  group_by(Output_name, label)%>%
  summarize(label_ = sum(as.numeric(correct))/n())%>%
  as.data.frame() %>%
  reshape(idvar = "Output_name", timevar = "label", direction = "wide") %>%
  remove_rownames() %>%
  column_to_rownames(var = "Output_name")
  

eval_mat <- as.matrix(eval)
class(eval_mat) <- "numeric"

```

# visualize evaluation per label
```{r}
library(ComplexHeatmap)
library(circlize)
library(viridis)


col_fun = colorRamp2(c(0,0.5,1), c("white", "red", "darkred"))
anno_fun = colorRamp2(c(0,1), c("white","darkgreen"))
label_mean = colMeans(eval_mat)
model_mean <- rowMeans(eval_mat)
colAnno <- columnAnnotation(label_mean = label_mean, col = list(label_mean = anno_fun))
rowAnno <- rowAnnotation(model_mean = model_mean, col = list(model_mean = anno_fun), show_legend=c(F))

Heatmap(eval_mat, row_title = "Model Output", show_column_dend = T, show_row_dend = T,col= col_fun, right_annotation = rowAnno, top_annotation = colAnno)

```

correlation between crop_input_size and prediction accuracy, aswell as dependency on cell size
```{r}
library(ggplot2)

# compute correct predicted cells per label per crop_input_size
ggplot(results, aes(x = crop_input_size, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```

dependency on cell size
```{r}
# TODO: add crop_input_size information

ggplot(results%>%
         group_by(label,crop_input_size)%>%
         summarise(radius = mean(sqrt(area/pi)),accuracy = sum(correct)/n(), crop_input_size = unique(crop_input_size))%>%
         filter(label!=-1),
       aes(x = radius, y= accuracy, col = as.factor(crop_input_size)))+
  geom_point() +
  theme_bw() +
  geom_smooth(method="lm")
```


__Output_2 gets almost as much right as a combination of models, but as most cells are tumor cells, we want to determine which models have non-overlaping strength in respect to the label__

```{r}

ggplot(results, aes(x = label, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~Output_name)


# hm_list <- NULL
# hm_sublist <- NULL
# 
# for (i in 1:dim(fractions)[3]){
#   hm <- Heatmap(fractions[,,i], col = col_fun, show_heatmap_legend=F, cluster_rows = F,cluster_columns = F,column_title=dimnames(fractions)[[3]][i])
#   
#   
#   hm_sublist <- hm_sublist + hm
#   
#   if (i%%3 == 0){
#     if(is.null(hm_list)){hm_list <- hm_sublist}
#     else{
#       hm_list <- hm_list %v% hm_sublist
#       hm_sublist <- NULL
#     }
#   }
# }
# 
# hm_list

```

