---
title: "multiclass classification ensemble analysis"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# Set path
if (Sys.info()["sysname"] == "Darwin"){
  mount_path <- "/Volumes/"
} else if (Sys.info()["sysname"] == "Linux"){
  mount_path <- "/mnt/"
} else {
  stop("Operating system is not supported")
}
```


load data
```{r}
sce <- readRDS(paste0(mount_path,"immucan_volume/processed_data/Panel_1/cell_classification/sce_selected.rds"))

# import merged results created with unified_ensemble.py
df <- read.csv(paste0(mount_path,"immucan_volume/processed_data/Panel_1/CellSighter/Multiclass/merged_ensemble.csv"))
df$X <- NULL
```


```{r}
library(stringr)
library(dplyr)
library(tidyverse)
# create unique cell id for all cells
df$unique_id <- paste0(df$image_id, df$cell_id)
sce$unique_id <- paste0(str_split(sce$image,".tiff", simplify = T)[,1],sce$ObjectNumber)

# merge data with sce and sort
results <- as.data.frame(colData(sce)) %>%
  inner_join(df, by= intersect(colnames(df),colnames(colData(sce))))

# create dictionary for translation between cell type id and cell type label
# create label to label-id dictionary, set unlabeled to -1
dic <- c()
labels <- sort(unique(sce$cell_labels))
labels <- labels[labels != "unlabelled"]

for (i in 1:length(labels)){
  dic[as.character(i-1)] <- labels[[i]]
}
dic["-1"] <- "unlabelled"

results$pred <- dic[as.character(results$pred)]
results$label <- dic[as.character(results$label)]

# add results to sce
sce <- sce[,sce$unique_id %in% results$unique_id]

for (feature in colnames(results)){
  if (!feature %in% colnames(colData(sce))){
    colData(sce)[,feature] <- results[,feature]
  }
}
```

Confusion matrix
```{r, fig.height=3,fig.width=3}
library(caret)




cm <- confusionMatrix(as.factor(results$pred), as.factor(results$label),
                mode = "everything")

data.frame(cm$byClass) %>%
    mutate(class = sub("Class: ", "", rownames(cm$byClass))) %>%
    ggplot() + 
    geom_point(aes(1 - Specificity, Sensitivity, 
                   size = Detection.Rate,
                   fill = class),
               shape = 21) + 
    scale_fill_manual(values = metadata(sce)$colour_vectors$cell_types) + 
    theme_bw() +
    theme(text = element_text(size = 10)) +
    ylab("Sensitivity (TPR)") +
    xlab("1 - Specificity (FPR)")

conf_matrix <- t(t(cm$table)/colSums(cm$table))
f1_scores <- cm$byClass[,"F1"]
```


```{r}
library(ComplexHeatmap)
library(circlize)
library(viridis)


col_fun = colorRamp2(c(0,1), c("white","red"))
col_anno <- columnAnnotation(f1 = f1_scores, col = list(f1 = col_fun),
                             F1 = anno_text(sprintf("%.2f", f1_scores), location = 0.5, just = "center",rot = 0, gp = gpar(fontsize = 10)))

hm <- Heatmap(conf_matrix, col = viridis(100),
              column_title = "Label",
              row_title = "CellSighter",
              cluster_rows = F,
              cluster_columns = F,
              bottom_annotation = col_anno,
              column_names_side = "top",
              heatmap_legend_param = list(at = c(0,0.2,0.4,0.6,0.8,1)),
              show_heatmap_legend = F,
              #column_title = dimnames(conf_matrix)[[3]][i],
              cell_fun = function(j, i, x, y, width, height, fill){
                grid.text(sprintf("%.2f", conf_matrix[i, j]), x, y, gp = gpar(fontsize = 10))})

hm
```

Individual model analysis
```{r}
# load results
per_model <- lapply(list.dirs(paste0(mount_path,"immucan_volume/processed_data/Panel_1/CellSighter/Multiclass/")),function(x){
  if(file.exists(paste0(x,"/val_results.csv"))){
    output <- str_extract(x,"Model_[0-9]{1,2}")
    df <- read.csv(paste0(x,"/val_results.csv"))
    df$Output_name <- rep(output,nrow(df))
    df <- df[,-c(1)]
    return (df)
    }
  }
)

per_model <- bind_rows(per_model)
per_model$label <- as.character(per_model$label)
per_model$pred <- dic[as.character(per_model$pred)]
per_model$label <- dic[as.character(per_model$label)]
```

```{r}
cm_list <- lapply(unique(per_model$Output_name), function(model){
  df <- per_model[per_model$Output_name == model,]
  cm <- confusionMatrix(as.factor(df$pred), as.factor(df$label),
                mode = "everything")
  
  cm_df <- data.frame(cm$byClass) %>%
    mutate(Output_name = rep(model,nrow(cm$byClass))) %>%
    mutate(class = sub("Class: ", "", rownames(cm$byClass)))
  return (cm_df)
})

cm_df <- bind_rows(cm_list)
  
  
cm_df%>%
  filter(class != "unlabelled") %>%
  ggplot() + 
  geom_point(aes(1 - Specificity, Sensitivity, 
                 size = Detection.Rate,
                 fill = class),
             shape = 21) + 
  scale_fill_manual(values = metadata(sce)$colour_vectors$cell_types) + 
  theme_bw() +
  facet_wrap(~Output_name) +
  ylab("Sensitivity (TPR)") +
  xlab("1 - Specificity (FPR)")
```

Prepare for spatial characterization of wrong labelled cells
```{r}
library(imcRtools)

# create label-prediction column
sce$label_pred <- paste0(sce$label,"_", sce$pred)
sce$correct <- as.numeric(sce$label == sce$pred)

sce <- buildSpatialGraph(sce, "image", type = "expansion", threshold = 20,
                         coords = c("Pos_X","Pos_Y"))

sce <- aggregateNeighbors(sce, "expansion_interaction_graph", count_by = "label")

sce <- aggregateNeighbors(sce, "expansion_interaction_graph", aggregate_by = "expression",
                          assay_type = "exprs")

assay <- t(as.matrix(sce$mean_aggregatedExpression[,rownames(sce)]))
colnames(assay) <- colnames(sce)
assay[is.na(assay)] <- 0
assay(sce, "mean_neighbor_expression") <- assay

```

__deper look into the high FPR of tumor and mural cells__ 
```{r}
fpr <- results %>%
  filter((pred == "Mural" | pred == "Tumor") & (pred != label))

table(fpr$label, fpr$pred)

```

Expression matrix of cells wrongly classified as tumor cells
```{r, fig.height=15, fig.width=10}
library(scuttle)
library(dittoSeq)


sce_tumor <- sce[,sce$pred == "Tumor" & sce$label != "Tumor" & sce$label != "unlabelled"]
wrong_tumor <- aggregateAcrossCells(sce_tumor, sce_tumor$label, statistics = "mean", use.assay.type = "exprs")


dittoHeatmap(sce_tumor, 
             genes = rownames(sce_tumor)[rowData(sce_tumor)$use_channel],
             assay = "exprs", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = "label", "pred",
             order.by = "label")

dittoHeatmap(wrong_tumor,
             genes = rownames(wrong_tumor),
             assay = "exprs", scale = "none",
             heatmap.colors = viridis(100),
             cell.names.meta = "label",
             cluster_cols = TRUE
             )
```

Expression matrix of cells wrongly classified as mural cells
```{r, fig.height=15, fig.width=10}
sce_mural <- sce[,sce$pred == "Mural" & sce$label != "Mural" & sce$label != "unlabelled"]
wrong_mural <- aggregateAcrossCells(sce_mural, sce_mural$label, statistics = "mean", use.assay.type = "exprs")


dittoHeatmap(sce_mural, 
             genes = rownames(sce_mural)[rowData(sce_mural)$use_channel],
             assay = "exprs", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("label", "pred","Indication"),
             order.by = "label")

dittoHeatmap(wrong_mural, 
             genes = rownames(wrong_mural),
             assay = "exprs", scale = "none",
             heatmap.colors = viridis(100),
             cell.names.meta = "label",
             cluster_cols = TRUE
             )
```

Compare expression of wrongly classified cells to correctly classified expression
```{r, fig.height=10, fig.width=10}
for (ct in unique(sce$cell_labels)){
  cur_sce <- sce[,startsWith(sce$label_pred,paste0(ct,"_"))]
  
  agg <- aggregateAcrossCells(cur_sce, cur_sce$label_pred, statistics = "mean", use.assay.type = "exprs")
  
  dittoHeatmap(agg, 
             main = paste(unique(agg$label)),
             genes = rownames(agg)[rowData(agg)$use_channel],
             assay = "exprs", scale = "none",
             heatmap.colors = viridis(100),
             cell.names.meta = "label_pred",
             cluster_cols = TRUE
             )
  
}

```

```{r, fig.height=30, fig.width=15}
library(BiocNeighbors)
library(BiocParallel)
library(scater)
library(cowplot)

cur_sce <- sce[,sce$cell_labels != "unlabelled"]

plot_list <- list()
count <- 0

len <- length(unique(cur_sce$cell_labels))
for (i in seq(1,len-1)){
  for (j in seq(i+1,len)){
    ct1 <- unique(cur_sce$cell_labels)[i]
    ct2 <- unique(cur_sce$cell_labels)[j]
    
    correct_ct1 <- paste0(ct1,"_",ct1)
    correct_ct2 <- paste0(ct2,"_",ct2)
    between_1 <- paste0(ct1,"_",ct2)
    between_2 <- paste0(ct2, "_", ct1)

    cur <- cur_sce[,(cur_sce$label_pred == correct_ct1) | (cur_sce$label_pred == correct_ct2) | (cur_sce$label_pred == between_1) | (cur_sce$label_pred == between_2) ]
    
    cur <- runUMAP(cur, exprs_values = "exprs", 
                     subset_row = !(grepl("DNA|Histone", rownames(cur))),
               external_neighbors = TRUE, BNPARAM = AnnoyParam(),
               BPPARAM = MulticoreParam(RNGseed = 12345))

    plot <- dittoDimPlot(cur, var = "label_pred",
               reduction.use = "UMAP", size = 0.2,
               do.label = TRUE) +
      ggtitle(paste0(ct1," - ", ct2))
    
      count <- count + 1
    plot_list[[count]] <- plot
    names(plot_list)[count] <- paste0(ct1," - ", ct2)
  }
}

plot_grid(plotlist = plot_list, ncol = 4)
```



Compare environmental expression of wrongly classified cells to correctly classified
```{r, fig.height=10, fig.width=10}
for (ct in unique(sce$cell_labels)){
  cur_sce <- sce[,startsWith(sce$label_pred,paste0(ct,"_"))]
  
  agg <- aggregateAcrossCells(cur_sce, cur_sce$label_pred, statistics = "mean", use.assay.type = "mean_neighbor_expression")
  
  dittoHeatmap(agg, 
             main = paste(unique(agg$label)),
             genes = rownames(agg)[rowData(agg)$use_channel],
             assay = "mean_neighbor_expression", scale = "none",
             heatmap.colors = viridis(100),
             cell.names.meta = "label_pred",
             cluster_cols = TRUE
             )
  
}

```

Compare environment of correctly labeled cells to the environment of wrongly labeled ones

```{r, fig.height=10, fig.width=10}
library(BiocNeighbors)
library(BiocParallel)
library(scater)

cur_sce <- sce[,sce$cell_labels != "unlabelled"]

plot_list_env <- list()
count <- 0

len <- length(unique(cur_sce$cell_labels))
for (i in seq(1,len-1)){
  for (j in seq(i+1,len)){
    ct1 <- unique(cur_sce$cell_labels)[i]
    ct2 <- unique(cur_sce$cell_labels)[j]
    
    correct_ct1 <- paste0(ct1,"_",ct1)
    correct_ct2 <- paste0(ct2,"_",ct2)
    between_1 <- paste0(ct1,"_",ct2)
    between_2 <- paste0(ct2, "_", ct1)

    cur <- cur_sce[,(cur_sce$label_pred == correct_ct1) | (cur_sce$label_pred == correct_ct2) | (cur_sce$label_pred == between_1) | (cur_sce$label_pred == between_2) ]
    
    cur <- runUMAP(cur, exprs_values = "mean_neighbor_expression", 
                     subset_row = !(grepl("DNA|Histone", rownames(cur))),
               external_neighbors = TRUE, BNPARAM = AnnoyParam(),
               BPPARAM = MulticoreParam(RNGseed = 12345))

    plot <- dittoDimPlot(cur, var = "label_pred",
               reduction.use = "UMAP", size = 0.2,
               do.label = TRUE) +
      ggtitle(paste0(ct1," - ", ct2))
    
    count <- count + 1
    plot_list_env[[count]] <- plot
  }

}

plot_grid(plotlist = plot_list_env, ncol = 4)

```

TODO:  compute distance in expression, environment, and cell type fraction (for all markers and only relevant markers)

compute distance between cells of incorrect label to correct label and predicted label in expression space
```{r}
euclidean_dist <- function(x, y) sqrt(sum((x - y)^2))


df <- as.data.frame(t(assay(cur_sce, "exprs"))) %>%
  select(-c(DNA1, DNA2, HistoneH3))

df$pred <- cur_sce$pred
df$label <- cur_sce$label
df$label_pred <- cur_sce$label_pred
df$correct <- cur_sce$correct

# compute mean expression value of correctly labeled cells per celltype
label_mean <- df%>%
  filter(correct == 1) %>%
  group_by(label) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE))) %>%
  select(-c(correct))

df <- df%>%
  left_join(label_mean, by = "label", suffix = c("_cell","_label"))

label_mean <- label_mean %>%
  rename_with(~ paste0(.x, "_pred"))

df <- df %>%
  left_join(label_mean, by = join_by("pred" == "label_pred"))


distances_to_label <- c()
distances_to_pred <- c()
for (i in 1:nrow(df)){
  cell <- df[i,] %>%
    select(ends_with("_cell")) %>%
    as.numeric()
  
  label <- df[i,] %>%
    select(ends_with("_label")) %>%
    as.numeric()
  
  pred <- df[i,] %>%
    select(ends_with("_pred")) %>%
    select(-c(label_pred)) %>%
    as.numeric()
    
  
  dist_to_label <- euclidean_dist(cell,label)
  dist_to_pred <- euclidean_dist(cell,pred)
  
  distances_to_label <- c(distances_to_label, dist_to_label)
  distances_to_pred <- c(distances_to_pred, dist_to_pred)
}

df$dist_to_label <- distances_to_label
df$dist_to_pred <- distances_to_pred
 

expression_similarity <- df %>%
  filter(correct == 0) %>%
  group_by(label_pred) %>%
  summarise(label = unique(label), pred = unique(pred), dist_to_label = mean(dist_to_label), dist_to_pred = mean(dist_to_pred), n = n()) %>%
  mutate(similarity = dist_to_label - dist_to_pred, similar_to_prediction = similarity > 0)


ggplot(expression_similarity %>%
         filter(n > 10), aes(x=reorder(label_pred, similarity), y=similarity, fill = similar_to_prediction)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  # coord_flip() +
  facet_grid(~label, scales = "free_x", drop = TRUE) +
  xlab("label - prediction") +
  ggtitle("Label")

```
# cell type relevant markers
```{r}
markers <- list()

# tumor markers
markers[["Tumor"]] <- rownames(sce)[grepl(pattern = "Ecad|CD3|CarbonicAnhydrase|HLADR|MPO|CD20|CD303|CD38|SMA|PDGFRb",rownames(sce))]

markers[["MacCD163"]] <- rownames(sce)[grepl(pattern = "CD20|HLADR|CD3|CD303|CD38|CD7|CD163|CD11c",rownames(sce))]

markers[["HLADR"]] <- rownames(sce)[grepl(pattern = "CD20|HLADR|CD3|CD303|CD38|CD7|CD163|CD11c",rownames(sce))]

markers[["DC"]] <- rownames(sce)[grepl(pattern = "CD20|HLADR|CD3|CD303|CD38|CD7|CD163|CD11c",rownames(sce))]


markers[["pDC"]] <- rownames(sce)[grepl(pattern = "Ecad|CD303",rownames(sce))]

markers[["Neutrophil"]] <- rownames(sce)[grepl(pattern = "MPO|CD15",rownames(sce))]

markers[["plasma"]] <- rownames(sce)[grepl(pattern = "CD303|CD38|CD7|CD11c",rownames(sce))]


markers[["Mural"]] <- rownames(sce)[grepl(pattern = "CD3|Ecad|CD38|CD20|CD303|MPO|CD7|HLADR|SMA",rownames(sce))]


markers[["B"]] <- rownames(sce)[grepl(pattern = "CD20|CD3|CD11c|CD303",rownames(sce))]

markers[["BnT"]] <- rownames(sce)[grepl(pattern = "CD20|CD3|CD11c|CD303",rownames(sce))]

markers[["NK"]] <- rownames(sce)[grepl(pattern = "CD7|Ecad|CD3",rownames(sce))]

markers[["CD4"]] <- rownames(sce)[grepl(pattern = "CD3|CD20|CD11c|CD303|FOXP3|CD8|CD4",rownames(sce))]

markers[["CD8"]] <- rownames(sce)[grepl(pattern = "CD3|CD20|CD11c|CD303|FOXP3|CD8|CD4",rownames(sce))]

markers[["Treg"]] <- rownames(sce)[grepl(pattern = "CD3|CD20|CD11c|CD303|FOXP3",rownames(sce))]
```

in relevant marker space
```{r}
library(stringr)
df <- as.data.frame(t(assay(cur_sce, "exprs"))) %>%
  select(-c(DNA1, DNA2, HistoneH3))

df$id <- colnames(cur_sce)
df$pred <- cur_sce$pred
df$label <- cur_sce$label
df$label_pred <- cur_sce$label_pred
df$correct <- cur_sce$correct

# compute mean expression value of correctly labeled cells per celltype
label_mean <- df%>%
  filter(correct == 1) %>%
  group_by(label) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE))) %>%
  select(-c(correct))

df <- df%>%
  left_join(label_mean, by = "label", suffix = c("_cell","_label"))

label_mean <- label_mean %>%
  rename_with(~ paste0(.x, "_pred"))

df <- df %>%
  left_join(label_mean, by = join_by("pred" == "label_pred"))


distances_to_label <- c()
distances_to_pred <- c()
for (i in 1:nrow(df)){
  
  row <- df[i,]
  relevant_markers <- markers[[row$label]]
  
  row <- row[,str_split(colnames(row),"_",simplify = TRUE)[,1] %in% relevant_markers]
  
  cell <- row %>%
    select(ends_with("_cell")) %>%
    as.numeric()
  
  label <- row %>%
    select(ends_with("_label")) %>%
    as.numeric()
  
  pred <- row %>%
    select(ends_with("_pred")) %>%
    as.numeric()
    
  
  dist_to_label <- euclidean_dist(cell,label)
  dist_to_pred <- euclidean_dist(cell,pred)
  
  distances_to_label <- c(distances_to_label, dist_to_label)
  distances_to_pred <- c(distances_to_pred, dist_to_pred)
}

df$dist_to_label <- distances_to_label
df$dist_to_pred <- distances_to_pred
 

expression_similarity <- df %>%
  filter(correct == 0) %>%
  group_by(label_pred) %>%
  summarise(label = unique(label), pred = unique(pred), dist_to_label = mean(dist_to_label), dist_to_pred = mean(dist_to_pred), n = n()) %>%
  mutate(similarity = dist_to_label - dist_to_pred, similar_to_prediction = similarity > 0)


ggplot(expression_similarity %>%
         filter(n > 10), aes(x=reorder(label_pred, similarity), y=similarity, fill = similar_to_prediction)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  # coord_flip() +
  facet_grid(~label, scales = "free_x", drop = TRUE) +
  xlab("label - prediction") +
  ggtitle("Label")
```



in environmental space
```{r}
df <- as.data.frame(cur_sce$mean_aggregatedExpression)

df$id <- colnames(cur_sce)
df$pred <- cur_sce$pred
df$label <- cur_sce$label
df$label_pred <- cur_sce$label_pred
df$correct <- cur_sce$correct

# compute mean expression value of correctly labeled cells per celltype
label_mean <- df%>%
  filter(correct == 1) %>%
  group_by(label) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE))) %>%
  select(-c(correct))

df <- df%>%
  left_join(label_mean, by = "label", suffix = c("_cell","_label"))

label_mean <- label_mean %>%
  rename_with(~ paste0(.x, "_pred"))

df <- df %>%
  left_join(label_mean, by = join_by("pred" == "label_pred"))


distances_to_label <- c()
distances_to_pred <- c()
for (i in 1:nrow(df)){
  cell <- df[i,] %>%
    select(ends_with("_cell")) %>%
    as.numeric()
  
  label <- df[i,] %>%
    select(ends_with("_label")) %>%
    as.numeric()
  
  pred <- df[i,] %>%
    select(ends_with("_pred")) %>%
    select(-c(label_pred)) %>%
    as.numeric()
    
  
  dist_to_label <- euclidean_dist(cell,label)
  dist_to_pred <- euclidean_dist(cell,pred)
  
  distances_to_label <- c(distances_to_label, dist_to_label)
  distances_to_pred <- c(distances_to_pred, dist_to_pred)
}

df$dist_to_label <- distances_to_label
df$dist_to_pred <- distances_to_pred
 

expression_similarity <- df %>%
  filter(correct == 0) %>%
  group_by(label_pred) %>%
  summarise(label = unique(label), pred = unique(pred), dist_to_label = mean(dist_to_label), dist_to_pred = mean(dist_to_pred), n = n()) %>%
  mutate(similarity = dist_to_label - dist_to_pred, similar_to_prediction = similarity > 0)


ggplot(expression_similarity %>%
         filter(n > 10), aes(x=reorder(label_pred, similarity), y=similarity, fill = similar_to_prediction)) +
  geom_bar(stat='identity') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  # coord_flip() +
  facet_grid(~label, scales = "free_x", drop = TRUE) +
  xlab("label - prediction") +
  ggtitle("Label")

```



```{r, fig.height=15, fig.width=10}
wrong_env <- sce[,(sce$pred != sce$label)  & (sce$label != "unlabelled")]
correct_env <- sce[,(sce$pred == sce$label)  & (sce$label != "unlabelled")]
# env_clusterd <- aggregateAcrossCells(wrong_env, wrong_env$label, statistics = "mean", use.assay.type = "exprs")

# aggregate across cell types
wrong_env_agg <- aggregateAcrossCells(wrong_env, wrong_env$label, statistics = "mean", use.assay.type = "mean_neighbor_expression")

correct_env_agg <- aggregateAcrossCells(correct_env, correct_env$label, statistics = "mean", use.assay.type = "mean_neighbor_expression")


dittoHeatmap(wrong_env, 
             genes = rownames(wrong_env)[rowData(wrong_env)$use_channel],
             assay = "mean_neighbor_expression", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("label", "pred","Indication"),
             order.by = "label")

dittoHeatmap(correct_env, 
             genes = rownames(correct_env)[rowData(correct_env)$use_channel],
             assay = "mean_neighbor_expression", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("label", "pred","Indication"),
             order.by = "label")


dittoHeatmap(wrong_env_agg, 
             genes = rownames(wrong_env_agg)[rowData(wrong_env_agg)$use_channel],
             assay = "mean_neighbor_expression", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("label", "pred","Indication"),
             order.by = "label")

dittoHeatmap(correct_env_agg, 
             genes = rownames(correct_env_agg)[rowData(correct_env_agg)$use_channel],
             assay = "mean_neighbor_expression", scale = "none",
             heatmap.colors = viridis(100),
             annot.by = c("label", "pred","Indication"),
             order.by = "label")
```


```{r}
library(ComplexHeatmap)


mural_mat <- as.data.frame(sce_mural$aggregatedNeighbors) %>%
  mutate(label = sce_mural$label) %>%
  group_by(label) %>%
  summarise_all(mean) %>%
  select(-c(unlabelled)) %>%
  column_to_rownames("label") %>%
  as.matrix()

mural_mat <- t(t(mural_mat)/colSums(mural_mat))

order <- rownames(mural_mat)
mural_mat <- mural_mat[,order]

Heatmap(mural_mat, col = viridis(100), cluster_rows = FALSE, cluster_columns = FALSE)

```





Predictions for unlabelled cells
```{r}
count_unlabelled <- table(results%>%
        filter(label == "unlabelled")%>%
        pull(pred))
freq_unlabelled <- count_unlabelled / sum(count_unlabelled)
count_cells <- table(results%>%
                       filter(label != "unlabelled")%>%
                       pull(label))
freq_cells <- count_cells / sum(count_cells)

m <- matrix(c(freq_unlabelled,freq_cells), nrow = 2, byrow=TRUE)
colnames(m) <- names(freq_cells)
rownames(m) <- c("unlabelled", "labels")


Heatmap(m)
```


