---
title: "Param sweep analysis"
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

# Set path
if (Sys.info()["sysname"] == "Darwin"){
  mount_path <- "/Volumes/"
} else if (Sys.info()["sysname"] == "Linux"){
  mount_path <- "/mnt/"
} else {
  stop("Operating system is not supported")
}
```

load in results from CellSighter and sce
```{r}
library(stringr)
library(dplyr)
library(SummarizedExperiment)
library(readxl)
library(tidyverse)

# load sce
sce <- readRDS(paste0(mount_path,"immucan_volume/processed_data/Panel_1/cell_classification/sce_selected.rds"))

# load results
results <- lapply(list.dirs(paste0(mount_path,"immucan_volume/processed_data/Panel_1/CellSighter/ParamSweep/")),function(x){
  if(file.exists(paste0(x,"/val_results.csv"))){
    output <- str_extract(x,"Model_[0-9]{1,2}")
    df <- read.csv(paste0(x,"/val_results.csv"))
    df$Output_name <- rep(output,nrow(df))
    df <- df[,-c(1)]
    return (df)
    }
  }
)

results <- bind_rows(results)
results$label <- as.character(results$label)

# load hyperparam dataframe
hyperparams <- read.csv("data/hyperparams.csv")
hyperparams$X <- NULL
rownames(hyperparams) <- hyperparams$Model_name
hyperparams$val_set <- as.factor(hyperparams$val_set)
hyperparams$crop_input_size <- as.factor(hyperparams$crop_input_sizue)
# correct spelling mistake
hyperparams$crop_input_sizue <- NULL
hyperparams$epoch_max <- as.factor(hyperparams$epoch_max)
hyperparams$lr <- as.factor(hyperparams$lr)


# create dictionary for translation between cell type id and cell type label
# create label to label-id dictionary, set unlabeled to -1
dic <- c()
labels <- sort(unique(sce$cell_labels))
labels <- labels[labels != "unlabelled"]

for (i in 1:length(labels)){
  dic[as.character(i-1)] <- labels[[i]]
}
dic["-1"] <- "unlabelled"

results$pred <- dic[as.character(results$pred)]
results$label <- dic[results$label]
```


```{r}
# create unique cell id for all cells
results$unique_id <- paste0(results$image_id, results$cell_id)
sce$unique_id <- paste0(str_split(sce$image,".tiff", simplify = T)[,1],sce$ObjectNumber)

# merge data with sce
results <- as.data.frame(merge(results,colData(sce),by="unique_id"))
```


Confusion matrix
```{r}
library(caret)

# filter unlabelled cells
results <- results %>%
  filter(label != "unlabelled")

sens_matrix <- matrix(rep(0, length(unique(results$Output_name))*length(unique(results$label))),nrow = length(unique(results$Output_name)), ncol = length(unique(results$label)))
spec_matrix <- matrix(rep(0, length(unique(results$Output_name))*length(unique(results$label))),nrow = length(unique(results$Output_name)), ncol = length(unique(results$label)))
f1_matrix <- matrix(rep(0, length(unique(results$Output_name))*length(unique(results$label))),nrow = length(unique(results$Output_name)), ncol = length(unique(results$label)))
conf_array <- array(rep(0,length(unique(results$label))*length(unique(results$label))*length(unique(results$Output_name))),
                    dim = c(length(unique(results$label)),length(unique(results$label)),length(unique(results$Output_name))),
                    dimnames = list(sort(unique(results$label)),sort(unique(results$label)),unique(results$Output_name))
                    )

sens_spec_plots <- vector('list', length(unique(results$Output_name)))

show = "none"
for (i in 1:length(unique(results$Output_name))){
  if (i == length(unique(results$Output_name))) show = "bottom"
  model <- unique(results$Output_name)[i]
  df <- results[results$Output_name == model,]
  cm <- confusionMatrix(as.factor(df$pred), as.factor(df$label),
                mode = "everything")
  
  sens_spec_plot <- data.frame(cm$byClass) %>%
    mutate(class = sub("Class: ", "", rownames(cm$byClass))) %>%
    ggplot() + 
    geom_point(aes(1 - Specificity, Sensitivity, 
                   size = Detection.Rate,
                   fill = class),
               shape = 21) + 
    scale_fill_manual(values = metadata(sce)$colour_vectors$cell_types) + 
    theme_bw() +
    ggtitle(model) +
    theme(legend.position = show) +
    ylab("Sensitivity (TPR)") +
    xlab("1 - Specificity (FPR)")
  
  sens_spec_plots[[i]] <- sens_spec_plot
  
  conf_matrix <- t(t(cm$table)/colSums(cm$table))
  f1_scores <- cm$byClass[,"F1"]
  sens_scores <- cm$byClass[,"Sensitivity"]
  spec_scores <- cm$byClass[,"Specificity"]
  
  conf_array[,,i] <- conf_matrix[sort(rownames(conf_matrix)),sort(rownames(conf_matrix))]
  f1_matrix[i,] <- f1_scores
  sens_matrix[i,] <- sens_scores
  spec_matrix[i,] <- spec_scores
}

colnames(f1_matrix) <- colnames(sens_matrix) <- colnames(spec_matrix) <- names(f1_scores)
rownames(f1_matrix) <- rownames(sens_matrix) <- rownames(spec_matrix)<- unique(results$Output_name)

```

```{r, fig.width=15, fig.height=15}
library(cowplot)

plot_grid(plotlist = sens_spec_plots)

```


```{r}
library(ComplexHeatmap)
library(circlize)
library(viridis)


col_fun = colorRamp2(c(0,1), c("white","red"))
col_fun2 = colorRamp2(c(0,1), c("white","blue"))

# hm_list <- NULL

for (i in 1:dim(conf_array)[3]){
  conf_matrix <- conf_array[,,i]
  # col_anno <- columnAnnotation(f1 = f1_matrix[i,], col = list(f1 = col_fun, Sensitivity = col_fun2, Specificity = col_fun2),
  #                              F1 = anno_text(sprintf("%.2f", f1_matrix[i,]), location = 0.5, just = "center",rot = 0),
  #                              Sensitivity = sens_matrix[i,],
  #                              Sens = anno_text(sprintf("%.2f", sens_matrix[i,]), location = 0.5, just = "center",rot = 0),
  #                              Specificity = spec_matrix[i,],
  #                              Spec = anno_text(sprintf("%.2f", spec_matrix[i,]), location = 0.5, just = "center",rot = 0))
  
  col_anno <- columnAnnotation(f1 = f1_matrix[i,], col = list(f1 = col_fun),
                               F1 = anno_text(sprintf("%.2f", f1_matrix[i,]), location = 0.5, just = "center",rot = 0))

  hm <- Heatmap(conf_matrix, col = viridis(100),
                cluster_rows = F,
                cluster_columns = F,
                bottom_annotation = col_anno,
                column_names_side = "top",
                heatmap_legend_param = list(at = c(0,0.2,0.4,0.6,0.8,1), title = "CM"),
                show_heatmap_legend = T,
                column_title = dimnames(conf_array)[[3]][i],
                cell_fun = function(j, i, x, y, width, height, fill){
                  grid.text(sprintf("%.2f", conf_matrix[i, j]), x, y, gp = gpar(fontsize = 10))})
  draw(hm)
  # hm_list <- hm_list + hm
}

```

visualize f1 scores
```{r, fig.width=15,fig.height=10}
library(RColorBrewer)

# get rid of na values in matrix
f1_matrix <- f1_matrix[,-c(1)]

col_vec_val_set = brewer.pal(name = "Set1", n = length(unique(hyperparams$val_set)))
names(col_vec_val_set) = unique(hyperparams$val_set)

col_vec_crop_input_size = brewer.pal(name = "Set2", n = length(unique(hyperparams$crop_input_size)))
names(col_vec_crop_input_size) = unique(hyperparams$crop_input_size)

col_vec_epoch_max = brewer.pal(name = "Set3", n = length(unique(hyperparams$epoch_max)))[1:2]
names(col_vec_epoch_max) = unique(hyperparams$epoch_max)

col_vec_lr = brewer.pal(name = "Accent", n = length(unique(hyperparams$lr)))[1:2]
names(col_vec_lr) = unique(hyperparams$lr)

col_vec_hierarchy = brewer.pal(name = "Dark2", n = length(unique(hyperparams$hierarchy_match)))[1:2]
names(col_vec_hierarchy) = unique(hyperparams$hierarchy_match)

                              

# create hyperparams row annotation
hyperparams$crop_input_size <- as.factor(hyperparams$crop_input_size)
ha = rowAnnotation(df = hyperparams[hyperparams$Model_name %in% rownames(f1_matrix),][rownames(f1_matrix),]%>%select(-Model_name),
                   col = list(val_set = col_vec_val_set,
                              crop_input_size = col_vec_crop_input_size,
                              epoch_max = col_vec_epoch_max,
                              lr = col_vec_lr,
                              hierarchy_match = col_vec_hierarchy
                              )
                   )

Heatmap(f1_matrix, show_column_dend = F, show_row_dend = T, left_annotation = ha,
        heatmap_legend_param = list(title = "F1"),
        col = col_fun,
        cell_fun = function(j, i, x, y, width, height, fill){
                  grid.text(sprintf("%.2f", f1_matrix[i, j]), x, y, gp = gpar(fontsize = 10))})

```
#TODO: add SCE information to the analysis and find correlations (cell type specific hyperparameters needed for OVA??)

correlation between crop_input_size and prediction accuracy, aswell as dependency on cell size
```{r}
library(ggplot2)

results <- results %>%
  mutate(correct = ifelse(pred == label, 1, 0))

results <- merge(results, hyperparams, by.x = "Output_name", by.y = "Model_name")

# compute correct predicted cells per label per crop_input_size
ggplot(results, aes(x = crop_input_size, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```

dependency on cell size
```{r}
# TODO: add crop_input_size information

ggplot(results%>%
         group_by(label,crop_input_size)%>%
         summarise(radius = mean(sqrt(area/pi)),accuracy = sum(correct)/n(), crop_input_size = unique(crop_input_size))%>%
         filter(label!=-1),
       aes(x = radius, y= accuracy, col = as.factor(crop_input_size)))+
  geom_point() +
  theme_bw() +
  geom_smooth(method="lm")


ggplot(results%>%
         group_by(label,crop_input_size)%>%
         summarise(radius = mean(sqrt(area/pi)),accuracy = sum(correct)/n(), crop_input_size = unique(crop_input_size))%>%
         filter(!label%in%c(-1,13)),
       aes(x = radius, y= accuracy, col = as.factor(crop_input_size)))+
  geom_point() +
  theme_bw() +
  geom_smooth(method="lm")
```

correlation between hierarchy_match and prediction accuracy, as well as dependency on label abundance
```{r}
# compute correct predicted cells per label per crop_input_size
ggplot(results, aes(x = hierarchy_match, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```


```{r}
ggplot(results %>%
  group_by(Output_name,label,hierarchy_match)%>%
  summarise(abundance = n(),acc = sum(correct)/n())%>%
    group_by(label,hierarchy_match)%>%
    summarise(abundance = mean(abundance), acc = mean(acc)),
  aes(x = log(abundance), y= acc, col = hierarchy_match))+
  geom_point() +
  geom_smooth(method = "lm")
```

#TODO: add epoch max and lr analysis

correlation between epoch_max and accuracy per cell type (do some cell Type profit more from more epochs than others?)
```{r}
# compute correct predicted cells per label per crop_input_size
ggplot(results, aes(x = epoch_max, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```
```{r}
ggplot(results%>%
         filter(label != -1) %>%
         group_by(label, epoch_max)%>%
         summarise(accuracy = sum(correct)/n(), label = unique(label)),
       aes(x = epoch_max, y = accuracy))+
  geom_boxplot()+
  geom_point(aes(col = label))
```

correlation between lr and accuracy per cell type (do some cell Type profit more higher lr than others?)
```{r}
# compute correct predicted cells per label per crop_input_size
ggplot(results, aes(x = lr, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```


```{r}
ggplot(results%>%
         filter(label != -1) %>%
         group_by(label, lr)%>%
         summarise(accuracy = sum(correct)/n(), label = unique(label)),
       aes(x = lr, y = accuracy))+
  geom_boxplot()+
  geom_point(aes(col = label))
```
optimal combination of lr and epoch max
```{r}
# compute correct predicted cells per label per crop_input_size
ggplot(results%>%
         group_by(epoch_max,lr,label)%>%
         mutate(id = paste0(lr,"_",epoch_max)),
       aes(x = id, fill = as.factor(correct)))+
  geom_bar(position = "fill") +
  labs(y = "Proportion")+
  facet_wrap(~label)
```

```{r}
ggplot(results%>%
         filter(label != -1) %>%
         group_by(epoch_max, lr, label)%>%
         summarise(accuracy = sum(correct)/n(), label = unique(label))%>%
         mutate(id = paste0(lr,"_",epoch_max)),
       aes(x = id, y = accuracy))+
  geom_boxplot()+
  geom_point(aes(col = label))
```
# TODO:
